\titel

### 2014-03-10 presentation/presa.tex
Remove FF-Replan vs. RFF slide

What if picking up a block fails?

@@

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again. Can the planner keep re- planning forever i.e. end up in deadlock? ''

@@

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again. Can the planner keep re- planning forever i.e. end up in deadlock? ''
   \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Planning under uncertainty: FF-Replan vs. RFF}

  \begin{itemize}
    \item
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item
    \item FF-Replan introduced MDP determinization to use classical planner with uncertainty
    \item RFF used this idea to generate policies using aggregation and Monte-Carlo simulations.
    \item FF-Replan has been improved with hindsight
    \item RFF has been improved for Hybrid Probabilistic Domains
    \item Also Determinizing of POMDPs have appeared
  \end{itemize}

>>>>

    \uncover<2> {What if picking up a block fails?}

@@

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
    \item ``FF-Replan planner replans the same determinization of the problem when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again. Can the planner keep re- planning forever i.e. end up in deadlock?''

@@

@@

@@

  \begin{itemize}
    \item FF-Replan introduced MDP determinization to use classical planner with uncertainty
    \item RFF used this idea to generate policies using aggregation and Monte-Carlo simulations.
    \item FF-Replan has been improved with hindsight
    \item RFF has been improved for Hybrid Probabilistic Domains
    \item Also Determinizing of POMDPs have appeared
  \end{itemize}
